---
title: "The relation between migration non-Western background and education level"
author: "Tamara Bakker 2695715, Rik de Bruijn 2894496, Joep Hagendoorn 2893599, Lize den Hertog 2889649, Isabelle Stankovski 2883224"
date: "`r Sys.Date()`"
output: pdf_document
---

# Set-up your environment

```{r package_install, include=FALSE}
#install.packages("tidyverse")
#install.packages("yaml")
#install.packages("rmarkdown")
#install.packages("readxl")
#install.packages("cbsodataR")
#install.packages("sf")
#install.packages("rnaturalearth")
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
remotes::install_github("ropensci/rnaturalearthhires")
install.packages("tinytex")
library(tinytex)
tinytex::install_tinytex()
```

```{r packages, echo=FALSE}
require(tidyverse)
require(rmarkdown)
require(yaml)
library(readxl)
library(cbsodataR)
library(sf)
library(rnaturalearth)
library(remotes)

```

# Title Page

Tamara Bakker, Rik de Bruijn, Joep Hagendoorn, Lize den Hertog and Isabelle Stankovski

Tutorial group 2-1

Fatima Amankour

# Part 1 - Identify a Social Problem

Use APA referencing throughout your document. [Here's a link to some explanation.](https://www.mendeley.com/guides/apa-citation-guide/)

## 1.1 Describe the Social Problem

A study by research agency SCALIQ involving 6409 secondary school students, suggests that students with Arabic first and/or last names are more likely to be placed at a lower educational level than equally intelligent student with European sounding names. About half of the students with Arabic names were placed half a school level lower. The researchers say that this may be a sign of inequality in education. However, the study only looks at intelligence and names. It did not look at other factors such as family income, home support or cultural background. The experts say that being placed in a lower school level that is too low can hurt students' education, confidence/motivation and career opportunities.

# Part 2 - Data Sourcing

## 2.1 Load in the data

```{r loading_data, echo=FALSE}
edu_mig_dataset <-read.csv("data/Jaar_bevolking_migratie_achtergrond.csv", sep=";")
reg_mig_dataset <- read_xlsx("data/Ranglijst van de migratieachtergrond van inwoners per provincie in Nederland.xlsx")
reg_edu_dataset <- read_xlsx("data/Regionale_kerncijfers_Nederland_04062026_120418.xlsx")
```

## 2.2 Provide a short summary of the dataset(s)

### Summary dataset on education level and migration background

In the first dataset about education level and migration background you can see that a group consisting of both men and women was researched. All of the men and women are 15 years old and above. In the dataset you can see the different migration backgrounds with the highest level of education achieved.

```{r echo=FALSE}
summary(edu_mig_dataset)
```

### Summary dataset on migration background percentage per region

```{r echo=FALSE}
summary(reg_mig_dataset)
```

### Summary dataset on education level per region

```{r echo=FALSE}
summary(reg_edu_dataset)
```

```{r}
inline_code = TRUE
```

These are things that are usually included in the metadata of the dataset. For your project, you need to provide us with the information from your metadata that we need to understand your dataset of choice.

## 2.3 Describe the type of variables included

Think of things like:

- Do the variables contain health information or SES information?

- Have they been measured by interviewing individuals or is the data coming from administrative sources?

*For the sake of this example, I will continue with the assignment...*

# Part 3 - Quantifying

## 3.1 Data cleaning

### Renaming unclear characters in edu_mig_dataset

```{r data_cleaning, echo=FALSE}
edu_mig_dataset <-read.csv("data/Jaar_bevolking_migratie_achtergrond.csv", sep=";")
edu_mig_dataset$Geslacht <-replace(edu_mig_dataset$Geslacht,edu_mig_dataset$Geslacht == "T001038", "totaal mannen en vrouwen")


edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd, str_detect(edu_mig_dataset$Leeftijd, "20150",), "15 jaar of ouder")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd=="21600", "75 jaar of ouder")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd=="52052","15 tot 75 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd=="53050","15 tot 25 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd== "53500","25 tot 35 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd== "53700", "35 tot 45 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd== "53800", "45 tot 55 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd=="53900","55 tot 65 jaar")
edu_mig_dataset$Leeftijd <- replace(edu_mig_dataset$Leeftijd,edu_mig_dataset$Leeftijd=="53925","65 to 75 jaar")

edu_mig_dataset$Migratieachtergrond <- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond== "1012600", "Nederlandse achtergrond")
edu_mig_dataset$Migratieachtergrond <- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond== "2012605","Met migratieachtergrond")
edu_mig_dataset$Migratieachtergrond <- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="2012655","Westerse migratieachtergrond")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond, edu_mig_dataset$Migratieachtergrond== "2012657","Niet-westerse migratieachtergrond")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="2012659","onbekende migratieachtergrond")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="T001040","Totaal")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="H008673","Marokko")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="H008766","Turkije")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="H008751", "Suriname")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond=="H007119","(voormalige) Nederlandse Antillen, Aruba")
edu_mig_dataset$Migratieachtergrond<- replace(edu_mig_dataset$Migratieachtergrond,edu_mig_dataset$Migratieachtergrond== "A008187","Overige niet-westerse migratieachgergrond ")

edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2003JJ00","2003")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2004JJ00","2004")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2005JJ00","2005")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2006JJ00","2006")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2007JJ00","2007")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2008JJ00","2008")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2009JJ00","2009")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2010JJ00","2010")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2011JJ00","2011")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2012JJ00","2012")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden, edu_mig_dataset$Perioden=="2013JJ00","2013")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2014JJ00","2014")
edu_mig_dataset$Perioden<-replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2015JJ00","2015")
edu_mig_dataset$Perioden<-replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2016JJ00","2016")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2017JJ00","2017")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2018JJ00","2018")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2019JJ00","2019")
edu_mig_dataset$Perioden<- replace(edu_mig_dataset$Perioden,edu_mig_dataset$Perioden=="2020JJ00","2020")

edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018710","Basisonderwijs")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<- replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                       edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018720",
                                                       "Vmbo-g/t, havo-, vwo-onderbouw")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                      edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018760",
                                                      "Mbo2 en mbo3")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                      edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018770",
                                                      "Mbo4")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                      edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018780",
                                                      "Havo, vwo")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                      edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018800",
                                                      "Hbo-, wo-bachelor")
edu_mig_dataset$HoogstBehaaldOnderwijsniveau<-replace(edu_mig_dataset$HoogstBehaaldOnderwijsniveau,
                                                      edu_mig_dataset$HoogstBehaaldOnderwijsniveau=="2018810",
                                                      "Hbo-,wo-master,doctor")


```

### Eliminating unnecessary observations and variables in edu_mig_dataset

```{r data_cleaning, echo=FALSE}
edu_mig_dataset_cl <- edu_mig_dataset %>% filter(Migratieachtergrond == "Totaal" | Migratieachtergrond == "Nederlandse achtergrond" | Migratieachtergrond == "Niet-westerse migratieachtergrond")
edu_mig_dataset_cl <- edu_mig_dataset_cl %>% select(-Geslacht)
```

### Renaming inconsistent characters in reg_edu_dataset

```{r data_cleaning, echo=FALSE}
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Zeeland (PV)", "Zeeland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Fryslân (PV)", "Friesland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Drenthe (PV)", "Drenthe")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Flevoland (PV)", "Flevoland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Limburg (PV)", "Limburg")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Overijssel (PV)", "Overijssel")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Gelderland (PV)", "Gelderland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Groningen (PV)", "Groningen")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Noord-Brabant (PV)", "Noord-Brabant")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Noord-Holland (PV)", "Noord-Holland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Zuid-Holland (PV)", "Zuid-Holland")
reg_edu_dataset$`Regio's`<- replace(reg_edu_dataset$`Regio's`, reg_edu_dataset$`Regio's`== "Utrecht (PV)", "Utrecht")
```

### Eliminating unnecessary years in reg_edu_dataset

```{r data_cleaning, echo=FALSE}
reg_edu_dataset_cl <- reg_edu_dataset %>%
  filter(Perioden > 2023 & Perioden< 2025)
```

### Eliminating unnecessary variables in reg_mig_dataset

```{r data_cleaning, echo=FALSE}
reg_mig_dataset_cl <- reg_mig_dataset %>% select("Provincienaam", "% Herkomst Nederland", "% Herkomst buiten Europa")
```

## 3.2 Generate necessary variables

Variable 1: Percentage of the total of Dutch people and non-European migrants in each level of education

```{r gen_var1, echo=FALSE}
new_var_1 <- edu_mig_dataset_cl %>%
  filter(
    Leeftijd            == "15 jaar of ouder",
    Migratieachtergrond %in% c("Nederlandse achtergrond", "Niet-westerse migratieachtergrond")
  ) %>%
  mutate(
    jaar   = as.integer(Perioden),
    niveau = factor(HoogstBehaaldOnderwijsniveau, levels = c(
      "Hbo-,wo-master,doctor",
      "Hbo-, wo-bachelor",
      "Havo, vwo",
      "Mbo4",
      "Mbo2 en mbo3",
      "Vmbo-g/t, havo-, vwo-onderbouw",
      "Basisonderwijs"
    ))
  ) %>%
  group_by(jaar, Migratieachtergrond, niveau) %>%
  summarise(bevolking = sum(Bevolking_1, na.rm = TRUE), .groups = "drop") %>%
  group_by(jaar, Migratieachtergrond) %>%
  mutate(pct = bevolking / sum(bevolking) * 100) %>%
  ungroup()

```

Variable 2: Percentage of non-European migrants that have obtained a hbo or wo bachelor for different age groups in 2020

```{r gen_var2, echo=FALSE}
# Code for percentage per age group of non-Western migrants that have obtained a hbo or wo bachelor
new_var_2 <- edu_mig_dataset_cl %>% filter(Perioden == 2020 & Migratieachtergrond == "Niet-westerse migratieachtergrond", Leeftijd %in% c("25 tot 35 jaar", "35 tot 45 jaar", "45 tot 55 jaar", "55 tot 65 jaar", "65 tot 75 jaar", "75 jaar of ouder")) %>% group_by(Leeftijd, HoogstBehaaldOnderwijsniveau == "Hbo-, wo-bachelor") %>% summarise(high_education_mig = sum(Bevolking_1, na.rm = TRUE), .groups = "drop") %>% group_by(Leeftijd) %>% mutate(percentage = high_education_mig / sum(high_education_mig) * 100) %>% ungroup() 
new_var_2 <- new_var_2 %>% filter(`HoogstBehaaldOnderwijsniveau == "Hbo-, wo-bachelor"` == TRUE)
new_var_2 <- new_var_2 %>% select(-`HoogstBehaaldOnderwijsniveau == "Hbo-, wo-bachelor"`)

# Code for percentage per age group of Dutch people that have obtained a hbo or wo bachelor
in_between_df <- edu_mig_dataset_cl %>% filter(Perioden == 2020 & Migratieachtergrond == "Nederlandse achtergrond", Leeftijd %in% c("25 tot 35 jaar", "35 tot 45 jaar", "45 tot 55 jaar", "55 tot 65 jaar", "65 tot 75 jaar", "75 jaar of ouder")) %>% group_by(Leeftijd, HoogstBehaaldOnderwijsniveau == "Hbo-, wo-bachelor") %>% summarise(high_education_nl = sum(Bevolking_1, na.rm = TRUE), .groups = "drop") %>% group_by(Leeftijd) %>% mutate(percentage = high_education_nl / sum(high_education_nl) * 100) %>% ungroup() 
in_between_df <- in_between_df %>% filter(`HoogstBehaaldOnderwijsniveau == "Hbo-, wo-bachelor"` == TRUE)

# Get them together in one dataset
new_var_2 <- new_var_2 %>% mutate(group = "Non-Western")
in_between_df <- in_between_df %>% mutate(group = "Dutch")
combined_var <- bind_rows(new_var_2, in_between_df)

# Clean the combined product
combined_var <- combined_var %>% select(Leeftijd, percentage, group)
```

## 3.3 Visualize temporal variation

Make own variable that shows our relation and plot it over time. Line graph with other version of migration-education dataset.

```{r echo=FALSE}

# Bevolking kolom naar numeriek
edu_mig_dataset$Bevolking_1 <- as.numeric(trimws(edu_mig_dataset$Bevolking_1))

# Kleuren van laag naar hoog
kleuren <- c(
  "Basisonderwijs"                 = "#d73027",
  "Vmbo-g/t, havo-, vwo-onderbouw" = "#f46d43",
  "Mbo2 en mbo3"                   = "#fdae61",
  "Mbo4"                           = "#fee090",
  "Havo, vwo"                      = "#9ecae1",
  "Hbo-, wo-bachelor"              = "#74add1",
  "Hbo-,wo-master,doctor"          = "#4575b4"
)

ggplot(new_var_1, aes(x = jaar, y = pct, fill = niveau)) +
  geom_area(stat = "identity", position = "fill", na.rm = TRUE) +
  facet_wrap(~ Migratieachtergrond, ncol = 2) +
  scale_fill_manual(values = kleuren) +
  scale_x_continuous(breaks = seq(2003, 2020, by = 2)) +
  scale_y_continuous(
    labels = scales::percent,
    expand = c(0, 0)
  ) +
  labs(
    title    = "Highest level of education based on migration background",
    subtitle = "Popultion 15 year of older, 2003–2020  |  source: CBS (EBB, tabel 82275NED)",
    x        = NULL,
    y        = "population share (%)",
    fill     = "education level"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position  = "bottom",
    strip.text       = element_text(face = "bold", size = 12),
    axis.text.x      = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    plot.title       = element_text(face = "bold"),
    panel.spacing    = unit(2, "lines")
  )



```

## 3.4 Visualize spatial variation

Compare/merge two maps, one with the level of education of a province and one with the proportion of migrants/people with a migration background living there. use datasets on migration background per region and education level per region to make maps. requires separate package, preferably from CBS. test effe

```{r}
# Kolomnamen opslaan
basis_col <- "Onderwijs|Naar woonregio|Hoogstbehaald onderwijsniveau|Basisonderwijs, vmbo, mbo1 (%)"

nl_map_data  <- ne_countries(country = "Netherlands", returnclass = "sf")
nl_provinces <- ne_states(country = "Netherlands", returnclass = "sf")

# Herstel namen naar Nederlands
nl_provinces$name <- recode(nl_provinces$name,
  "North Brabant" = "Noord-Brabant",
  "South Holland" = "Zuid-Holland",
  "North Holland" = "Noord-Holland"
)

# Join
spatial_var_edu <- right_join(nl_provinces, reg_edu_dataset_cl, by = c("name" = "Regio's"))

# Plot
ggplot(spatial_var_edu) +
  geom_sf(aes(fill = .data[[basis_col]])) +
  scale_fill_gradient(low = "#fff7bc", high = "#d95f0e") +
  labs(
    title = "Percentage of population with primary education or lower (per province)",
    fill  = "% Primary / vmbo / mbo1"
  ) +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))




# Laad kaartdata
nl_map_data  <- ne_countries(country = "Netherlands", returnclass = "sf")
nl_provinces <- ne_states(country = "Netherlands", returnclass = "sf")

# Herstel namen naar Nederlands
nl_provinces$name <- recode(nl_provinces$name,
  "North Brabant" = "Noord-Brabant",
  "South Holland" = "Zuid-Holland",
  "North Holland" = "Noord-Holland"
)

# Join
spatial_var_mig <- right_join(nl_provinces, reg_mig_dataset_cl, by = c("name" = "Provincienaam"))

# Plot
ggplot(spatial_var_mig) +
  geom_sf(aes(fill = `% Herkomst buiten Europa`)) +
  scale_fill_gradient(low = "#e8f5e9", high = "#1b5e20") +
  labs(
    title = "Percentage of population with non-Western migration background",
    fill  = "% Non-western"
  ) +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
```

Here you provide a description of why the plot above is relevant to your specific social problem.

## 3.5 Visualize sub-population variation

Comparison between the difference in education level between different ages, use dataset migration education and either a histogram or bar plot.

```{r visualise_subpopulations, echo=FALSE}
ggplot(combined_var, aes(x = Leeftijd, y = percentage, fill = group)) + geom_col(position = "dodge", na.rm = TRUE, colour = "black") + scale_fill_manual(values = c("Dutch" = "lightpink", "Non-Western" = "#E75480")) + labs( title = "Proportion of people that have a hbo or wo bachelor per age group", y = "Percentage (of people)", x = "Age group") + theme_minimal()
```

Here you provide a description of why the plot above is relevant to your specific social problem.

## 3.6 Event analysis

Find some kind of event in order to show changes caused by this event: Analyze the relationship between two variables. will be a line graph, not sure which dataset yet.

```{r analysis, echo=FALSE}
# Filter alleen basisonderwijs + niet-westerse achtergrond
event_data <- new_var_1 %>%
  filter(
    niveau == "Basisonderwijs",
    Migratieachtergrond == "Niet-westerse migratieachtergrond"
  )

# Plot
ggplot(event_data, aes(x = jaar, y = pct)) +
geom_line(color = "steelblue", linewidth = 1) +
geom_point(color = "steelblue", size = 2) +
  geom_vline(xintercept = 2006, linetype = "dashed", color = "black") +
  annotate("text", x = 2006.2, y = max(event_data$pct),
           label = "introduction Wet inburgering (2006)", hjust = 0, size = 3.5) +
  labs(
    title = " Share of people with a non-western migrationbackground with primary school as there highest education level over the years",
    x     = "Year",
    y     = "Percentage of Non western migrants with primary school as highest education (%)"
  ) +
  scale_x_continuous(breaks = unique(event_data$jaar)) +
  theme_minimal() +
  theme(
    plot.title  = element_text(face = "bold", size = 13),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

Here you provide a description of why the plot above is relevant to your specific social problem.

# Part 4 - Discussion

## 4.1 Discuss your findings

Discuss the findings from all the analyses and draw somewhat of a conclusion whether our hypothesis was right. \# Part 5 - Reproducibility make sure that if someone were to reproduce our work, a change in packages would not matter as the information of which packages we used when is clear. \## 5.1 Github repository link

Provide the link to your PUBLIC repository here: ...

## 5.2 Reference list

Use APA referencing throughout your document.
