---
title: "Correlation between migration background and education level"
author: "Tamara Bakker 2695715, Rik de Bruijn 2894496, Joep Hagendoorn 2893599, Lize den Hertog 2889649, Isabelle Stankovski"
date: "`r Sys.Date()`"
output: pdf_document
---

# Set-up your environment

```{r package_install, include=FALSE}
#install.packages("tidyverse")
#install.packages("yaml")
#install.packages("rmarkdown")
#install.packages("readxl")

```

```{r packages}
require(tidyverse)
require(rmarkdown)
require(yaml)
library(readxl)
```

# Title Page

Tamara Bakker, Rik de Bruijn, Joep Hagendoorn, Lize den Hertog and Isabelle Stankovski

Tutorial group 2-1

Fatima Amankour

# Part 1 - Identify a Social Problem

Use APA referencing throughout your document. [Here's a link to some explanation.](https://www.mendeley.com/guides/apa-citation-guide/)

## 1.1 Describe the Social Problem

Explain why this is is a social problem and what the problem is.

# Part 2 - Data Sourcing

## 2.1 Load in the data

Preferably from a URL, but if not, make sure to download the data and store it in a shared location that you can load the data in from. Do not store the data in a folder you include in the Github repository!

```{r loading_data}
edu_mig_dataset <-read.csv("data/Jaar_bevolking_migratie_achtergrond.csv", sep=";")
reg_mig_dataset <- read_xlsx("data/Ranglijst van de migratieachtergrond van inwoners per provincie in Nederland.xlsx")
reg_edu_dataset <- read_xlsx("data/Regionale_kerncijfers_Nederland_04062026_120418.xlsx")
```

midwest is an example dataset included in the tidyverse package

## 2.2 Provide a short summary of the dataset(s)

### Summary dataset on education level and migration background

```{r}
summary(edu_mig_dataset)
```

### Summary dataset on migration background percentage per region

```{r}
summary(reg_mig_dataset)
```

### Summary dataset on education level per region

```{r}
summary(reg_edu_dataset)
```

In this case we see 28 variables, but we miss some information on what units they are in. We also don't know anything about the year/moment in which this data has been captured.

``` r
inline_code = TRUE
```

These are things that are usually included in the metadata of the dataset. For your project, you need to provide us with the information from your metadata that we need to understand your dataset of choice.

## 2.3 Describe the type of variables included

Think of things like:

- Do the variables contain health information or SES information?

- Have they been measured by interviewing individuals or is the data coming from administrative sources?

*For the sake of this example, I will continue with the assignment...*

# Part 3 - Quantifying

## 3.1 Data cleaning

Say we want to include only larger distances (above 2) in our dataset, we can filter for this.

```{r data_cleaning}
mean(dataset$percollege)
```

Please use a separate 'R block' of code for each type of cleaning. So, e.g. one for missing values, a new one for removing unnecessary variables etc.

## 3.2 Generate necessary variables

Variable 1

```{r gen_var1}

```

Variable 2

```{r gen_var2}

```

## 3.3 Visualize temporal variation

Make own variable that shows our relation and plot it over time. Line graph with other version of migration-education dataset.

```{r}

```

## 3.4 Visualize spatial variation

Compare/merge two maps, one with the level of education of a province and one with the proportion of migrants/people with a migration background living there. use datasets on migration background per region and education level per region to make maps. requires separate package, preferably from CBS.

```{r visualise_map}

```

Here you provide a description of why the plot above is relevant to your specific social problem.

## 3.5 Visualize sub-population variation

Comparison between the difference in education level between different ages, use dataset migration education and either a histogram or bar plot.

```{r visualise_subpopulations}
dataset$inmetro <- dataset$inmetro %>% as.factor()
# Boxplot of poverty rate by state using the 'midwest' dataset
ggplot(dataset, aes(x = inmetro, y = percadultpoverty)) +
  geom_boxplot() +
  labs(
    title = "Distribution of Poverty Rates by Metropolitan status (Midwest counties)",
    x = "Metropolitan Area",
    y = "Poverty Rate of Adults (%)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right"
  )


```

Here you provide a description of why the plot above is relevant to your specific social problem.

## 3.6 Event analysis

Find some kind of event in order to show changes caused by this event: Analyze the relationship between two variables. will be a line graph, not sure which dataset yet.

```{r analysis}

```

Here you provide a description of why the plot above is relevant to your specific social problem.

# Part 4 - Discussion

## 4.1 Discuss your findings

Discuss the findings from all the analyses and draw somewhat of a conclusion whether our hypothesis was right. \# Part 5 - Reproducibility make sure that if someone were to reproduce our work, a change in packages would not matter as the information of which packages we used when is clear. \## 5.1 Github repository link

Provide the link to your PUBLIC repository here: ...

## 5.2 Reference list

Use APA referencing throughout your document.
